---
title: "p8105_hw5_zj2357"
author: "Zekai Jin"
date: "2022-11-14"
output: github_document
---

First of all, we should include  the libraries we are using and prepare the dataset.
```{r init, message=FALSE}
library(tidyverse)
knitr::opts_chunk$set(
  message  = FALSE,
  warning = FALSE,
  fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
```

# Problem 1
read and tidy the data
```{r}
f_names = list.files("data", pattern = "(exp|con)_\\d\\d.csv")

joined_df = 
  map_dfr(str_c("data/",f_names),read_csv) %>%
  mutate(
    id = str_replace(f_names, ".csv", ""),
    group = as.factor(str_replace(f_names, "_\\d\\d.csv", ""))
  ) %>%
  select(id, group, everything()) 

write_csv(joined_df, "data/tidy/result.csv")
```

Making a spaghetti plot
```{r}
joined_df %>%
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "value"
  ) %>%
  mutate(week = as.numeric(week)) %>%
  ggplot(aes(x = week,y = value, color = group, group = id)) +
  geom_line()
```
According to the plot, the observation of the experiment arm was similar to the control arm in week 1. However, as time goes by, their value gradually increased, and became higher than all individuals in the control arm.

# Problem 2
Loading the dataset and summarize the crime cases over city.
```{r}
rm(list = ls())

homi_df = 
  read_csv("data/homicide-data.csv") %>%
  mutate(
    city_state = str_c(city, ",", state) 
  ) %>%
  group_by(city_state) %>%
  summarise(
    n_obs = n(),
    unsolved = sum(disposition %in% c("Closed without arrest","Open/No arrest"))
  )
```


```{r}

  
homi_filt = filter(homi_df,city_state == "Baltimore,MD")
test_res =  prop.test(x = homi_filt$unsolved, n = homi_filt$n_obs)
save(test_res, file = "results/prop_test_BMD.RData")
broom::tidy(test_res) %>%
  select(estimate, conf.low,conf.high)
```

```{r}
conf_int =
  map2_df(.x = homi_df$unsolved, .y = homi_df$n_obs, .f =  ~broom::tidy(prop.test(.x,.y))) %>%
  mutate(city_state = homi_df$city_state) %>%
  select(city_state, estimate, conf.low,conf.high)

conf_int
```

```{r}
conf_int %>%
  mutate(
    city_state = fct_reorder(city_state, -estimate)
  ) %>%
  ggplot(aes(x = estimate, y = city_state)) +
  geom_point()+
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high))
```



# Problem 3

```{r}
rm(list=ls())

prop_rej <- function(u = 0, sigma = 5, n = 30, n_dataset = 5000){
  dataset = map(.x = rep(u, n_dataset), .f = ~tibble(data=rnorm(n,.x,sigma))) %>%
    map(t.test) %>%
    map_df(broom::tidy)

  p_rej = dataset %>%
    filter(p.value < 0.05)%>%
    nrow() %>%
    `/`(n_dataset)

  u_est = dataset %>%
    pull(estimate) %>%
    mean()
  
  u_rej = dataset %>%
    filter(p.value < 0.05) %>%
    pull(estimate) %>%
    mean()
  
  tibble(u=u, p_rej = p_rej, u_est = u_est, u_rej = u_rej)
}


# iterating over u = 0:6
exp_res = 
  0:6 %>%
  map_df(prop_rej)
```


```{r}
exp_res %>%
  ggplot(aes(x=u,y=p_rej)) +
  geom_line() +
  scale_y_continuous(labels = scales::percent_format(scale = 100)) +
  scale_x_continuous(breaks = 0:6)+
  ylab("percentage of rejection")+
  labs(title = "Percentage of Rejection over Different u")
```


```{r}
exp_res %>%
  pivot_longer(
    u_est:u_rej,
    names_to = "u_type",
    values_to = "u_est"
  ) %>%
  ggplot(aes(x=u,y=u_est, color = u_type)) +
  geom_line() +
  scale_color_discrete(labels = c("all", "rejected"))+
  scale_x_continuous(breaks = 0:6)+
  ylab("estimated u")+
  labs(title = "Comparasion of estimated between all and rejected samples")
```


